---
title: "hw4"
output: html_document
date: "2023-12-06"
---
```{r, echo = FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, cache = FALSE)
options(warn = -1)
```

Tuocheng Chen
tchen465@wisc.edu

The successful attempts are pearson correlation and Euclidean distance. \
In fact as each time the cut dataframe is standardized (and the base data), 
the two standards are exactly the same! \
Let base be X and cut be Y. \
$\Sigma X_i^2 = n, \Sigma Y_i^2 = n, \Sigma X_i = 0, \Sigma Y_i = 0$.

Correlation is $\Sigma X_iY_i /n$, 
Euclidean is $\sqrt{2n-2\Sigma X_iY_i}$

I chose to use the Euclidean.

Used CHTC to run the R-script on all the tgz files, each with 1 job, and output a csv of its top 100, 

merged all the results to get the top 100 of all files:hw4best100.csv.

Load the data and the csv and select the best 10. Plot them alongside the true data.

Rescaled the base and the fits to make the plots more obvious.

Difficulties: when transfer_input_files are incomplete, it does not run successfully.

Below are the plots

```{r, echo=FALSE}
require("FITSio")
```

```{r}
rm(list=ls())
data <- read.csv("hw4best100.csv")
data = data[1:10,]
```

```{r}
#read in the fits files
best <- list()
number <- 10
lengths <- rep(0,number)
for (j in 1:number){
  best[[j]] <- readFrameFromFITS(paste("./data/",data$spectrumID[j],sep=""))
  best[[j]]$index <- 1:nrow(best[[j]])
}
base <- readFrameFromFITS("./data/cB58_Lyman_break.fit")
colnames(base)<-c("loglam","flux")
base$index <- 1:nrow(base)
```

```{r}
# Define plotting function
myplot <- function(j) {
  #adjust the scales
  # both mean 0
  #same var as sample
    bestflux = best[[j]]
    base1 <- base
    m1 = mean(bestflux$flux)
    s1 = sd(bestflux$flux)
    m2 = mean(base1$flux)
    s2 = sd(base1$flux)
    bestflux$flux = (bestflux$flux - m1)/s1
    base1$flux = (base1$flux - m2)/s2

    spectrumID <- sub("^[0-9]{4}/", "", gsub("\\.fits$", "", data$spectrumID[j]))
    plot(bestflux$flux, type = "l", col = "blue", xlab = "Index", ylab = "Rescaled Flux", 
         main = paste("cB58 and ", spectrumID, sep = ""), xlim = c(1, nrow(bestflux)), ylim=c(-4,4))
    lines(seq(data$i[j], data$i[j] + length(base1$flux) - 1), base1$flux, type = "l", col = "red")
    legend("topright", legend = c(spectrumID, "cB58"), col = c("blue", "red"), lty = 1)
}

```

Use `myplot(i)` to plot the i th plot. Order adjusted to 2-1-3-5-7-4-6-8-9-10

```{r, echo=FALSE}
myplot(2)
```
```{r, echo=FALSE}
myplot(1)
```
```{r, echo=FALSE}
myplot(3)
```
```{r, echo=FALSE}
myplot(5)
```
```{r, echo=FALSE}
myplot(7)
```
```{r, echo=FALSE}
myplot(4)
```
```{r, echo=FALSE}
myplot(6)
```
```{r, echo=FALSE}
myplot(8)
```
```{r, echo=FALSE}
myplot(9)
```
```{r, echo=FALSE}
myplot(10)
```



